---
title: 2019-nCoV Epidemic Mitigation Time Forecast (2020-02-07)
date: 2020-02-07
slug: predict-2020-02-07
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, error = FALSE, collapse = TRUE, out.width = "100%")
Sys.setlocale('LC_CTYPE', 'Chinese')
```

```{r}
require(ncovr)
ncovChina <- get_ncov('china') 
ncovChina <- ncovChina[ncovChina[, "日期"] <= as.Date('2020-02-07'), ]
```

## Time trends and model predictions of confirmed cases across the country

```{r}
predict_date(province = "中国",  ncov = ncovChina)
pre <- predict_date(province = "中国",  ncov = ncovChina, ifplot = FALSE)
```

Our model shows that the national epidemic situation will ease on `r pre$enddate` (the number of confirmed cases will not increase significantly).

On 2020-`r pre$tomorrow` there will be `r format(round(pre$tomorrowNew), scientific = FALSE)` new confirmed cases and in total `r format(round(pre$tomorrowcount), scientific = FALSE)` confirmed cases.

## National Epidemic Time Series

<small>

```{r}
ncovChina <- ncovChina[rev(order(ncovChina[, 1])), ]
knitr::kable(ncovChina[, 1:9], format = "html", row.names = FALSE, col.names = c('Date', 'Confirmed', 'Suspected', 'Severe', 'Dead', 'Cured', 'Conf.+Susp.', 'Incr. in Conf.+ Susp.', 'Under Obs.'))
```

</small>


```{r}
ncov <- get_ncov()
ncov$area$date <- as.Date(ncovr:::conv_time(ncov$area$updateTime))
ncov$area <- ncov$area[ncov$area$date < as.Date('2020-02-07'), ]
df_predict <- t(sapply(unique(ncov$area$provinceShortName[ncov$area$country == '中国']), function(x) predict_date(province = x, ncov = ncov, ifplot = FALSE)))

df_predict <- as.data.frame(df_predict)
df_predict <- df_predict[order(-as.numeric(df_predict$tomorrowNew)), ]
tomorrow <- df_predict$tomorrow[1]
```

```{r, results='asis'}
cat("## 2020-02-07 Epidemic forecast by province")
```

```{r}
knitr::kable(df_predict[!is.na(df_predict$enddate), c(1, 2, 5, 4)], format = "html", row.names = FALSE, col.names = c("Provinces", "Epidemic Mitigation Time", paste0(tomorrow, "Daily increase in confirmed"), paste0(tomorrow, "Confirmed in total")))
```

```{r, results='asis'}
for(x in unique(ncov$area$provinceShortName)) {
  cat(x, ":  \n")
  predict_date(province = x, ncov = ncov, ifplot = TRUE, ifchinese = TRUE)
  cat("  \n")
}
```
