---
title: Overview of 2019-nCoV
slug: intro
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, error = FALSE)
Sys.setlocale('LC_CTYPE', 'Chinese')
```

## Introduction of the virus

Virus Type: New Coronavirus 2019-nCoV

Source of infection: patients who are already with new coronavirus infection. Asymptomatic patients can also be contagious.

Ways of Transmission: Respiratory droplets and contact transmission are the main ways of transmission. Other transmission ways such as aerosol and digestive tract are yet to be confirmed.

Vulnerable population: Generally susceptible to all population. Elderly people and those with chronic diseases are more sick after infection. Children, infants and young children also have symptoms
Incubation period: Generally 3 to 7 days, up to 14 days. Infectious during incubation period, and contagious cases with asymptomatic are very rare.

Host: Wild animal, possibly Rhinolophus sinicus. 


```{r, results='asis'}
require(ncovr)
ncov <- get_ncov()
ncov <- ncov$overall
```

## Latest data

```{r, results='asis'}
cat(
  'Confirmed: ', ncov$confirmedCount,  "  \n\n",
  'Suspected: ', ncov$suspectedCount,  "  \n\n",
  'Cured: ', ncov$curedCount,  "  \n\n",
  'Dead: ', ncov$deadCount,  "  \n\n",
  'Serious: ', ncov$seriousCount,  "  \n\n",
  'Daily increase of confirmed: ', ncov$confirmedIncr,  "  \n\n",
  'Daily increase of suspected: ', ncov$suspectedIncr,  "  \n\n",
  'Daily increase of cured: ', ncov$curedIncr,  "  \n\n",
  'Daily increase of dead: ', ncov$deadIncr,  "  \n\n",
  'Daily increase of serious: ', ncov$seriousIncr,  "  \n\n",
  'Updated: ', as.character(ncovr:::conv_time(ncov$updateTime))
)
```
The number of suspected cases comes from the National Health and Medical Commission's data, which is currently national-wide data.

## National Epidemic Time Series

<small>

```{r}
ncovChina <- get_ncov('china')
ncovChina <- ncovChina[rev(order(ncovChina[, 1])), ]

knitr::kable(ncovChina[, 1:9], format = "html", row.names = FALSE, col.names = c('Date', 'Confirmed', 'Suspected', 'Severe', 'Dead', 'Cured', 'Conf.+Susp.', 'Incr. in Conf.+ Susp.', 'Under Obs.'))
```

</small>

The following pictures are from dxy.cn.

```{r, out.width="100%"}
knitr::include_graphics(unlist(ncov$dailyPics))
```
